---
title: "RapidMiner Overview"
author: "Andrew Chisholm"
date: "1 February 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(xtable)
library(knitr)
```

## About me

- Andrew Chisholm
- Data Scientist and Product Manager
- Recent Master’s in Data Science
- Telecoms industry
- Certified RapidMiner Master – number 007
- Lots of R and occasionally Python
- Author and book editor
- Winner of a data mining competition

## Topics

* Installation
* GUI overview
* Terminology
* Making a process
* Running a process
* Other things

## Installation

* RapidMiner Studio
    + Download from RapidMiner.com
    + Installs on Windows, Mac and Linux
* Java version 8 required
* Community version is limited to 10,000 rows
* Other products also available – we won’t look at these today
    + RapidMiner Server
    + Radoop – Hadoop for RapidMiner

## GUI Overview

```{r, results = 'asis', echo = F}

topics = data.frame(topics = c(
'Process',
'Operators',
'Parameters',
'Repository',
'Help',
'Panels',
'Re-arranging panels',
'Results view',
'Import/export process',
'XML view',
'Marketplace',
'Sub-processes',
'Debugging',
'Ordering of operators',
'Database connections',
'Comments',
'Spark/Radoop',
'Cloud'))
kable(topics)
```
some words

## Terminology - remember these

* Process → a collection of operators performing a task
* Operator → a small piece of functionality that performs a distinct action
* Example set → Data
* Example → a single row of an example set
* Attribute → a column in an example set
* Label → a known value that is associated with an example and which is to be predicted

## Making a process

* Drag data from repository
* Connect output