---
title: "RapidMiner Overview"
author: "Andrew Chisholm"
date: "26 March 2019"
output: 
  ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(xtable)
library(knitr)
library(kableExtra)
```

## About me

- Andrew Chisholm
- Data Scientist and Product Manager
- Recent MSc in Data Science
- Telecoms industry
- Certified RapidMiner Master – number 007
- Lots of R and occasionally Python
- Author and book editor
- Winner of a data mining competition
- https://www.linkedin.com/in/andrew-chisholm-72836b/

## Topics

* Installation
* GUI overview
* Terminology
* Rapidly making a prediction process
* Changing things
* Where to go next

## Installation

* RapidMiner Studio
    + Community version supports 10,000 rows
    + Follow the referral link below to get an extra 10,000 rows
    + Download from RapidMiner.com
    + Installs on Windows, Mac and Linux
    + Java version 8 required
* Other products also available – we won’t look at these today
    + RapidMiner Server
    + Radoop – Hadoop for RapidMiner
    
```
https://my.rapidminer.com/nexus/account/index.html#ref?id=vb41btp8dq9c
```

## Terminology - remember these

* **Process**: a collection of operators performing a task
* **Operator**: a small piece of functionality that performs a distinct action
* **Example set**: Data
* **Example**: a single row of an example set
* **Attribute**: a column in an example set
* **Label**: a known value that is associated with an example and which is to be predicted

## GUI Overview - bingo card

```{r, results = 'asis', echo = F}
topics = data.frame(
	t1 = c(
		'Process',
		'Operators',
		'Parameters',
		'Repository',
		'Help',
		'Panels',
		'Meta data'
		),
	t2 = c(
		'Re-arranging panels',
		'Results view',
		'Import/export process',
		'XML view',
		'Marketplace',
		'Sub-processes',
		'Building blocks'
		),
	t3 = c(
		'Debugging',
		'Ordering of operators',
		'Database connections',
		'Comments',
		'Spark/Radoop',
		'Cloud',
		'Replace operator'
		),
	t4 = c(
	  'Drag operators',
    'Finding operators',
		'Left click, right click',
		'Enable/Disable',
		'Connect operators',
		'Attribute roles',
		'Attribute types'
		
	  )
	)
colnames(topics) = NULL
kable(topics) %>% 
	kable_styling(bootstrap_options = 'striped', font_size = 22) %>%
	column_spec(1:4, width_max='2em', width_min = '2em')
#%>%#
#	row_spec(1:6, align = 'c')
```
```
https://imagebin.ca/v/4bX9qe3IBUp9
```

## Rapidly making a prediction process

* Simple process using the sonar data set
* 200 training examples: we will build a model using these
* 8 test examples: we will use the model to predict these
* We will build the process in stages
* We will include cross validation to estimate performance on unseen data

<div class="notes">
- Drag operators
- Finding operators
- Left click, right click
- Enable/Disable
- Connect operators
- Attribute roles
- Attribute types - nominal, real, integer, boolean, date
- Building blocks - easier than dragging operators
</div>

## Changing things

* It is easy to change things
    + Different models
    + Different performance measures
* Finding a better model
    + Forward selection
    + Evolutionary selection
* Manipulating the data
    + Change features
    + Select features
    
<div class="notes">
- Replace operator
- Example set meta data
</div>

## Where to go next

* These slides are here https://github.com/awchisholm/RapidMinerOverview 
* There is a lot of help out there
* RapidMiner has an active community 
* StackOverflow and CrossValidated
* Video material exists
    + Many videos on the RapidMiner site
    + RapidMinerResources - my content - a bit out of date now
* Blogs
    + https://rapidminernotes.blogspot.com/ - my geeky blog
* Books

