---
title: "RapidMiner Overview"
author: "Andrew Chisholm"
date: "1 February 2019"
output: 
  ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(xtable)
library(knitr)
library(kableExtra)
```

## About me

- Andrew Chisholm
- Data Scientist and Product Manager
- Recent MSc in Data Science
- Telecoms industry
- Certified RapidMiner Master – number 007
- Lots of R and occasionally Python
- Author and book editor
- Winner of a data mining competition
- https://www.linkedin.com/in/andrew-chisholm-72836b/

## Topics

* Installation
* GUI overview
* Terminology
* Making a process
* Running a process
* Other things

## Installation

* RapidMiner Studio
    + Download from RapidMiner.com
    + Installs on Windows, Mac and Linux
* Java version 8 required
* Community version is limited to 10,000 rows
* Other products also available – we won’t look at these today
    + RapidMiner Server
    + Radoop – Hadoop for RapidMiner

## GUI Overview

```{r, results = 'asis', echo = F}

topics = data.frame(
	t1 = c(
		'Process',
		'Operators',
		'Parameters',
		'Repository',
		'Help',
		'Panels'
		),
	t2 = c(
		'Re-arranging panels',
		'Results view',
		'Import/export process',
		'XML view',
		'Marketplace',
		'Sub-processes'
		),
	t3 = c(
		'Debugging',
		'Ordering of operators',
		'Database connections',
		'Comments',
		'Spark/Radoop',
		'Cloud'
		)
	)
colnames(topics) = NULL
kable(topics) %>% 
	kable_styling(bootstrap_options = 'striped', font_size = 26) %>%
	column_spec(1:3, width_max='2em', width_min = '2em') %>%
	row_spec(1:6, align = 'c')
```

## Terminology - remember these

* Process → a collection of operators performing a task
* Operator → a small piece of functionality that performs a distinct action
* Example set → Data
* Example → a single row of an example set
* Attribute → a column in an example set
* Label → a known value that is associated with an example and which is to be predicted

## Making a process

* Drag data from repository
* Connect output